%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Missions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Coach API/API proxy product owner - Devops reinforcement} % Job title
    {Orange} % Organization
    {Warsaw - Poland} % Location
    {Sept. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coach the current API team}
        \item {Share the concept of business API design}
        \item {Redesign the overall Api architecture around 3 main principles : data, security and developer experience}
        \item {Redesign and standardize the registration/login flow}
        \item {Enabling the Business Api as a product}
        \item {Improve the api security}
        \item {Enhance the microservice setup}
        \item {Develop and deploy a few microservice to boost up the delivery}
        \item {Share an internal API portal to enable api transparency, user account, api logs, etc..}
        \item {Enhance the continuous delivery strategy}
        \item {Built fully automated CI/CD pipelines on GoCd for critical components from dev to prod}
        \item {Support the mobile app team to implement the open id connect registration flow}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#Java ~
      \#GoCd ~
      \#Redis ~
      \#Kong ~
      \#Keycloak ~
      \#Rabbimq ~
      \#ReactNative ~
      \#MongoDb ~
      \#ElasticSearch ~
      \#Microservices ~
      \#Kibana ~
      \#Kubernetes ~
      \#OpenApi ~
      \#BDD
    }

%---------------------------------------------------------
  \cventry
    {Software Architect - API Product Owner} % Job title
    {Krungthai-Axa} % Organization
    {Bangkok - Thailand} % Location
    {Sept. 2016 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Active leader of the digital transformation team}
        \item {Implement the Company Business API based on a microservice architecture}
        \item {Drive the Business Api as a product}
        \item {Enable the business agility by providing a short feedback loop}
        \item {Design the overall Api architecture around 3 main principles : data, security and developer experience}
        \item {Share an internal API portal as the main source of truth by distributing the api contract, uml diagram, api logs, etc...}
        \item {Implement a contribution model around APIs. Share the api ownership across the stakholders, product owners or developers}
        \item {Speed up the continuous delivery practice by leveraging a chatops. From 1 release a month to 1 release a day}
        \item {Built fully automated CI/CD pipelines on GoCd for containerized applications using Docker, Openshift and Kubernetes.}
        \item {Implement continuous testing on production (Test the api contract, api gateway config and api behavior)}
        \item {Onboard and support new public api consumers}
        \item {Deploy a centralized monitoring environment(AppMetrics, Grafana, prometheus) which gather system metrics.}
        \item {Promote the data driven practice by leveraging the big data platform to monitor the api performance and suspicious request}
        \item {Build an extreme confidence within the team to release at any moment}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#NodeJs ~
      \#python ~
      \#Golang ~
      \#GoCd ~
      \#Redis ~
      \#Kong ~
      \#Keycloak ~
      \#Rabbimq ~
      \#Hadoop ~
      \#Oracle ~
      \#MsSql ~
      \#MongoDb ~
      \#ElasticSearch ~
      \#Microservices ~
      \#ContinousTesting ~
      \#Kibana ~
      \#Kubernetes ~
      \#Openshift ~
      \#OpenApi ~
      \#TDD ~
      \#BDD
    }

%---------------------------------------------------------
  \cventry
    {Technical Lead - Scrum Master} % Job title
    {Palo-It} % Organization
    {Singapore \& Bangkok - Thailand} % Location
    {Aug. 2015 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Agile coaching (Scrum Ceremonies, involving the B.U.)}
        \item {Lean startup methodology (improved the website conversion rate from 0.3\% to 25\%) }
        \item {Setup API middleware (NodeJs) to launch a Mobile app}
        \item {Include a Penetration tests step on the continuous integration pipeline}
        \item {Track metrics on every online product (Tag commander, Google Analytics, AT internet, Facebook pixel)}
        \item {Implement a digital analytics dashboard. (Google Analytics API, JIRA API, Jenkins API, NodeJs, Openshift)}
        \item {Technical training to the local team}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#Javascript ~
      \#NodeJs ~
      \#AngularJs ~
      \#Jenkins ~
      \#Docker ~
      \#TDD ~
      \#Jenkins ~
      \#Kubernetes ~
      \#Openshift
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Freelance Remote} % Job title
    {Satisfactory} % Organization
    {Paris - France} % Location
    {Sept. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Agile workshops}
        \item {Technical presentations}
        \item {Big Data Visualization}
        \item {Frontend application (AngularJs)}
        \item {Convert a monolith backend to an API micro-service (NodeJs, REST Api)}
        \item {Increase productivity by automating the test approach (unit test, functional test)}
        \item {Setup the deployment Industrialization (Capistrano, Jenkins, Docker)}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#php ~
      \#javascript ~
      \#AngularJs ~
      \#D3 ~
      \#Symphony2 ~
      \#Jenkins ~
      \#TDD 
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Buymeby} % Organization
    {New York city - USA} % Location
    {Sept. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build the MVP mobile app}
        \item {Lead the Front-end development department}
        \item {Create a backend API Micro services}
        \item {Growth Hacking Strategy: website scrapping, collected over 3,000 lead email contacts.}
        \item {Setup the deployment Industrialization}
      \end{cvitems}
    }
    {
      \#ptyhon ~
      \#Java ~
      \#NodeJs
      \#Android
      \#Firebase ~
      \#AngularJs ~
      \#googleApi ~
      \#Aws ~
    }

%---------------------------------------------------------
  \cventry
    {Software engineer - Freelance consultant} % Job title
    {Astria} % Organization
    {Paris - France} % Location
    {Aug. 2011 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop and contribute to multiple web application used by 200 000 customers}
        \item {Build and deploy a matching algorithm (1.5 M entries)}
        \item {Improve efficiency and quality of the software development}
        \item {Trained, mentored and motivated six new engineers}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#php ~
      \#java ~
      \#NodeJS ~
      \#AngularJs ~
      \#Zend ~
      \#Symfony2 ~
      \#Jenkins ~
      \#Ldap ~
      \#Oracle ~
      \#MsSql ~
      \#TDD
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& Software Engineer} % Job title
    {Vizzuel} % Organization
    {Paris - France} % Location
    {Sept. 2009 - Jul. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manage Web/Mobile development project}
        \item {Matching the technology to the business goals}
        \item {Setup the deployment Industrialization Key contributor in acquiring corporate contracts}
      \end{cvitems}
    }
    {
      \#php ~
      \#java ~
      \#CSharp ~
      \#AdobeFlash ~
      \#Jenkins ~
      \#Ldap ~
      \#Android ~
      \#WindowsPhone ~
      \#Blackberry ~
      \#Javascript
    }

%---------------------------------------------------------
\end{cventries}
